Verifying Demonstrations

### 2020-03-12 paper/DB-Schnorr-nbit.tex

>>>>

\paragraph{\Acl{DBTF}}

We cannot achieve \ac{DBTF} resistance.
Indeed, the prover can send \(l+\nu\) bits of both response strings, \(s_0\) 
and \(s_1\), to the adversary.
When the adversary receives the \(l+1\)th bit, he learns \(b\).
He can send \(b\) to the prover and answer correctly to the verifier, provided 
\(\nu \geq 1\).
By the time he receives the next challenge from the verifier, the prover will 
have sent him the remaining bits of \(s_b\) without revealing more bits about 
\(s_{1-b}\).
This would not taint the session.
As long as \(l+\nu\) is sufficiently small, the adversary cannot compute the 
remaining bits of \(s_{1-b}\) to compute the prover's secret.
